RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-11-01 overview.tex
formalframework cleanup & new example

A core aspect of the RationalGRL framework are the argument schemes, which should be close to the actual types of reasoning stakeholders or designers perform (requirement 1 of our framework). Recall from section \ref{sect:gmas} that we ended up with a list of argument schemes and critical questions that were found in the transcripts (Table~\ref{table:transcripts:results:argumentschemes}). Using this list as a basis, we further refined the set of argument schemes and critical questions for RationalGRL into the list shown in Table~\ref{table:argument-schemes}. Note that this list is not exhaustive, and that new argument schemes and critical questions can be added depending on the problem domain.

>>>>

A core aspect of the RationalGRL framework are the argument schemes, which should be close to the actual types of reasoning stakeholders perform (requirement 1). Recall from section \ref{sect:gmas} that we ended up with a list of argument schemes and critical questions that were found in the transcripts (Table~\ref{table:transcripts:results:argumentschemes}). Using this list as a basis, we further refined the set of argument schemes and critical questions for RationalGRL into the list shown in Table~\ref{table:argument-schemes}. Note that this list is not exhaustive, and that new argument schemes and questions can be added depending on the problem domain.
